miniKanren with fair search strategies

### 2019-04-09 Paper/paper.tex
newcommend conde

% Forget the issues about efficiency
% Read the monad paper

@@

Interleaving DFS, the search strategy of \texttt{cond$^e$} in
miniKanren~\citep{friedman_reasoned_2018}, allocates computational resource
by the order in which the claueses are written. Each clause of a
\texttt{cond$^e$} takes a half of the current resource and passes the other half
to its following clauses, except for the last clause that takes all of current
resource. 
both opportunity and burden: miniKanren users can place more frequently used 
goal at the beginning to optimize their programs; however, it might be a 
catastrophe if a goal that generate many useless states is placed before more 
important goals. Seasoned miniKanreners usually know how to utilize 
the unfairness to optimize their programs. However, we believe search strategies 
that is less sensitive to goal order can also be useful to little miniKanreners 
as well as seansoned ones. We propose two such search strategies, balanced 
interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they 
affect the efficiency and the answer order of known miniKanren programs. The 
experiment is conducted with the miniKanren from \textit{The Reasoned Schemer, 
2nd Edition}.

@@

A search strategy is \emph{fair} if answers of lower costs always come first. 
The \emph{cost} of an answer the number of relation applications needed to 
verify the answer. Now we illustrate the costs of answers by running a 
miniKanren relation. Fig.~\ref{def-repeato} defines the relation 
\texttt{repeato} that relates a term \texttt{x} with a list whose elements are 
all \texttt{x}s.

@@

With iDFS, \texttt{'(a a)} occurs before \texttt{'(b)} while \texttt{'(a a)} is 
associated with a higher cost. iDFS strategy is the cause, since it prioritizes 
the first \texttt{conde} case considerablely. When every \texttt{conde} case 
are equally productive, the iDFS strategy takes $1/2^{i}$ answers from the 
$i$-th case, except the last case, which share the same portion as the second 
last one. In contrast, the same run with BFS produces answers in an expected 
order.

@@

>>>>

\newcommand{\conde}{\texttt{cond$^e$} }

@@

Interleaving DFS, the search strategy of \conde in
miniKanren~\citep{friedman_reasoned_2018}, allocates computational resource
by the order in which the claueses are written. Each clause of a
\conde takes a half of the current resource and passes the other half
to its following clauses, except for the last clause that takes all of current
resource. 
both opportunity and burden: miniKanren users can place more frequently used 
goal at the beginning to optimize their programs; however, it might be a 
catastrophe if a goal that generate many useless states is placed before more 
important goals. Seasoned miniKanreners usually know how to utilize 
the unfairness to optimize their programs. However, we believe search strategies 
that is less sensitive to goal order can also be useful to little miniKanreners 
as well as seansoned ones. We propose two such search strategies, balanced 
interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they 
affect the efficiency and the answer order of known miniKanren programs. The 
experiment is conducted with the miniKanren from \textit{The Reasoned Schemer, 
2nd Edition}.

@@

A search strategy is \emph{fair} if answers of lower costs always come first. 
The \emph{cost} of an answer is the number of relation applications. Now we 
illustrate the costs of answers by running a miniKanren relation. 
Fig.~\ref{def-repeato} defines the relation \texttt{repeato} that relates a term 
\texttt{x} with a list whose elements are all \texttt{x}s.

@@

With iDFS, \texttt{'(a a)} occurs before \texttt{'(b)} while \texttt{'(a a)} is 
associated with a higher cost. iDFS strategy is the cause, since it prioritizes 
the first \conde case considerablely. When every \conde case 
are equally productive, the iDFS strategy takes $1/2^{i}$ answers from the 
$i$-th case, except the last case, which share the same portion as the second 
last one. In contrast, the same run with BFS produces answers in an expected 
order.

@@

%TODO contributions
%TODO future works
